---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# salty

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

When teaching students how toc elan data, it helps to have data that isn't _too_ clean already.
**salty** offers functions for "salting" clean data with problems often found in datasets in the wild, such as:

- pseudo-OCR errors
- inconsistent capitalization and spelling
- invalid dates
- unpredictable punctuation in numeric fields
- missing values or empty strings

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## Related work

https://github.com/paulhendricks/anonymizer

https://github.com/ropensci/charlatan

## Acknowledgements

The common OCR replacement errors are partially derived from the sed replacements specified in the [Royal Society Corpus project](http://fedora.clarin-d.uni-saarland.de/rsc/access.html): Knappen, Jörg, Fischer, Stefan, Kermes, Hannah, Teich, Elke, and Fankhauser, Peter. 2017. "The Making of the Royal Society Corpus." In _Proceedings of the NoDaLiDa 2017 Workshop on Processing Historical Language_. Göteborg, Sweden. Linköping University Electronic Press. <http://www.ep.liu.se/ecp/article.asp?issue=133&article=003&volume=>.
