---
output:
  md_document:
    variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# salty

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis-CI Build Status](https://travis-ci.org/mdlincoln/salty.svg?branch=master)](https://travis-ci.org/mdlincoln/salty)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdlincoln/salty?branch=master&svg=true)](https://ci.appveyor.com/project/mdlincoln/salty)
[![Coverage Status](https://img.shields.io/codecov/c/github/mdlincoln/salty/master.svg)](https://codecov.io/github/mdlincoln/salty?branch=master)

When teaching students how to clean data, it helps to have data that isn't _too_ clean already.
**salty** offers functions for "salting" clean data with problems often found in datasets in the wild, such as:

- pseudo-OCR errors
- inconsistent capitalization and spelling
- invalid dates
- unpredictable punctuation in numeric fields
- missing values or empty strings

## Installation

You can install salty from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdlincoln/salty")
```

## Usage

```{r example}
library(salty)
set.seed(10)

# We'll use charaltan to create some sample data

sample_names <- charlatan::ch_name(10)
sample_names

sample_numbers <- charlatan::ch_double(10)
sample_numbers
```

salty offers a few different ways of adding salt to your data: inserting, substituting, replacing, and deleting.

`salt_insert` keeps all the characters in the original while adding new ones, while `salt_substitute` overwrites those characters.

```{r}
# Use p to specify the percent of values that you would like to salt
salt_insert(sample_names, shaker$punctuation, p = 0.5)

# Use n to specify how many new insertions/substitutions you want to make to selected values
salt_substitute(sample_names, shaker$punctuation, p = 0.5, n = 3)
```

Different flavors of salt are available using `shaker`, however you can also supply your own character vector of possible replacements if you like.

```{r}
salt_insert(sample_names, shaker$mixed_letters, p = 0.5)

salt_insert(sample_numbers, shaker$digits, p = 0.5)

salt_insert(sample_names, c("foo", "bar", "baz"), p = 0.5)
```

`salt_replace` is a bit more targeted: it works with pairs of patterns and replacements, either contained in `replacement_shaker` or user-specified. Use `rep_p` to set a probability of how many possible replacements should actually get swapped out for any given value.

```{r}
salt_replace(sample_names, replacement_shaker$ocr_errors, p = 1, rep_p = 1)

salt_replace(sample_names, replacement_shaker$capitalization, p = 0.5, rep_p = 0.2)

salt_replace(sample_numbers, replacement_shaker$decimal_commas, p = 0.5, rep_p = 1)
```

`salt_delete` will simply drop characters, while `salt_empty` and `salt_na` will replace entire values.

```{r}
salt_delete(sample_names, p = 0.5, n = 6)

salt_empty(sample_names, p = 0.5)

salt_na(sample_names, p = 0.5)
```

## Related work

https://github.com/paulhendricks/anonymizer

https://github.com/ropensci/charlatan

## Acknowledgements

The common OCR replacement errors are partially derived from the sed replacements specified in the [Royal Society Corpus project](http://fedora.clarin-d.uni-saarland.de/rsc/access.html): Knappen, Jörg, Fischer, Stefan, Kermes, Hannah, Teich, Elke, and Fankhauser, Peter. 2017. "The Making of the Royal Society Corpus." In _Proceedings of the NoDaLiDa 2017 Workshop on Processing Historical Language_. Göteborg, Sweden. Linköping University Electronic Press. <http://www.ep.liu.se/ecp/article.asp?issue=133&article=003&volume=>.
